% ============================================================
% Englishom Development Report - Full Stack & DevOps
% Compiler: XeLaTeX (Recommended on Overleaf)
% ============================================================
\documentclass[11pt,a4paper]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{tcolorbox}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{fontspec}
\usepackage{polyglossia}

% Language Setup
\setmainlanguage{english}
\setotherlanguage{arabic}
\newfontfamily\arabicfont[Script=Arabic, Scale=1.1]{Amiri}
\newcommand{\arb}[1]{\textarabic{#1}}

% Custom Colors
\definecolor{darkblue}{RGB}{0,51,102}
\definecolor{lightblue}{RGB}{220,235,252}
\definecolor{examgreen}{RGB}{0,128,0}
\definecolor{arabicbg}{RGB}{255,248,230}
\definecolor{arabicframe}{RGB}{200,160,60}
\definecolor{highlightgold}{RGB}{245,187,65}

% Hyperlinks Setup
\hypersetup{
    colorlinks=true, 
    linkcolor=darkblue,
    urlcolor=highlightgold
}

% Header and Footer Setup
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{darkblue}{\textbf{Englishom -- Full Technical \& Features Report}}}
\fancyhead[R]{\textcolor{darkblue}{\thepage}}
\fancyfoot[C]{\textcolor{gray}{\small System Architecture \& Advanced Features | Phase 2 (May 21 - June 24, 2026)}}
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{darkblue}\leaders\hrule height \headrulewidth\hfill}}

% Title Formats
\titleformat{\section}{\LARGE\bfseries\color{darkblue}}{}{0em}{}[\color{darkblue}\titlerule]
\titleformat{\subsection}{\Large\bfseries\color{darkblue}}{}{0em}{}

% Custom Boxes
\newtcolorbox{topicbox}[1]{
    colback=lightblue, 
    colframe=darkblue, 
    fonttitle=\bfseries, 
    title={#1}, 
    boxrule=1.5pt, 
    arc=4pt
}
\newtcolorbox{arabicbox}{
    colback=arabicbg, 
    colframe=arabicframe, 
    boxrule=1pt, 
    arc=3pt, 
    left=5pt, 
    right=5pt
}

\begin{document}

% ============================================================
% TITLE PAGE
% ============================================================
\begin{titlepage}
\centering\vspace*{2cm}
{\Huge\bfseries\textcolor{darkblue}{Englishom Educational Platform}\par}\vspace{0.5cm}
{\LARGE\textcolor{darkblue}{Comprehensive Technical, Security \& UX Report}\par}\vspace{0.3cm}
{\Large\textcolor{gray}{System Upgrades, UI/UX Revamp, Translation \& Security}\par}\vspace{1.5cm}
\rule{\textwidth}{2pt}\vspace{0.5cm}
{\large Development Period: May 21, 2026 -- June 24, 2026\par}\vspace{0.3cm}
{\large Architecture: Full-Stack (React, Node.js, Nginx, MySQL, TypeScript)\par}\vspace{0.5cm}
\rule{\textwidth}{2pt}
\vspace{1.5cm}

\begin{arabicbox}
\begin{center}
\textbf{\Large \textarabic{التقرير الفني الشامل والموسع لكافة الأعمال والتطويرات لمنصة إنجليشوم}}\\[10pt]
\textarabic{هذا التقرير هو المرجع التقني الشامل الذي يوثق حرفياً كل تعديل وميزة تم برمجتها في المرحلة الثانية لتطوير المنصة. شملت هذه المرحلة مئات التعديلات المباشرة في واجهات المستخدم، قواعد البيانات، خوادم أباتشي، وتحسينات الأداء لحماية الإيرادات ورفع جودة المنصة لتنافس المنصات العالمية الكبرى.}
\end{center}
\end{arabicbox}

\vspace{1cm}
\begin{topicbox}{Project Scale \& Engineering Effort}
\begin{itemize}[leftmargin=*]
    \item \textbf{Total Engineering Activity:} 242+ Commits logged.
    \item \textbf{Codebase Volume:} Over 150,000 lines of code successfully added, modified, or refactored.
    \item \textbf{Microservices Handled:} 6 distinct applications fully merged (Ques, Dashboard, Blog, Test, Landing, Core).
\end{itemize}
\end{topicbox}

\end{titlepage}

\tableofcontents\newpage

% ============================================================
\section{1. Revenue Protection \& Zero-Day Vulnerability Patches}
% ============================================================

\begin{topicbox}{Data Leakage, Payment Integrity \& SQLi Defense}
\begin{itemize}[leftmargin=*]
\item \textbf{Course Access Bypass Patched (\texttt{level-access.service.ts}):} Fixed a massive flaw where pending/failed Paymob orders bypassed locks, allowing users to unlock paid courses for free. 
\item \textbf{API Answer Leakage Patched (\texttt{ques.controller.ts}):} Blocked endpoints from transmitting correct exam answers to the frontend client before the user actually submitted the test.
\item \textbf{IDOR \& SQL Injection Fixes:} Secured blog ratings with robust session validations (fixing IDOR) and refactored core database queries via Drizzle ORM's \texttt{inArray} to sanitize input against SQL injection attacks.
\item \textbf{Strict Admin Authentication:} Created strictly isolated authentication portals for administrators (\texttt{/api/admin/auth/login}), hiding control panels from brute-force bot attacks.
\item \textbf{White Screen Crash Fixes:} Resolved a silent failure in the \texttt{ques} application routing that previously caused the entire app to crash with a white screen on certain invalid requests.
\end{itemize}
\end{topicbox}
\begin{arabicbox}
\textbf{\textarabic{حماية الإيرادات وسد الثغرات الحرجة:}}\\
\textarabic{إغلاق ثغرة تخطي الدفع المجاني للكورسات، سد ثغرة تسريب إجابات الاختبارات وحماية جداول التقييمات من الاختراق. عزل لوحات الإدارة وإصلاح مشاكل انهيار التطبيقات بـ (الشاشة البيضاء) وتحصين قاعدة البيانات ضد هجمات الحقن} (\textenglish{SQL Injection})\textarabic{.}
\end{arabicbox}

% ============================================================
\section{2. UI/UX Revamp, Dashboard Rebuild \& Full Localization}
% ============================================================

\begin{topicbox}{Professional UI, RTL Alignment \& Full Localization}
\begin{itemize}[leftmargin=*]
\item \textbf{CMS Translation Engine (\texttt{i18n}):} Fully translated all admin panels (User Details, Admins Add/Update, Account Forms, Levels) to support flawless Arabic and English switching.
\item \textbf{Professional UI Replacement:} Stripped out all amateur emojis across the platform (Quiz results, landing pages, dashboards) and replaced them with crisp, professional \texttt{Lucide React} icons.
\item \textbf{Admin Dashboards Rebuild:} Completely rebuilt the Admin page with new tables, search/filter logic, expandable details, and fixed severe RTL (Right-to-Left) table column alignment issues.
\item \textbf{Dark Mode \& Styling Fixes:} Corrected access denied page colors in dark mode, resolved icon container overflow issues, fixed Tamara logo clipping, and addressed UI jitter during hover effects on feature cards.
\item \textbf{Test Results Features:} Engineered and added new Download \& Share functionality to the Quiz results page.
\end{itemize}
\end{topicbox}
\begin{arabicbox}
\textbf{\textarabic{إعادة بناء واجهات المستخدم والتعريب والتحسينات البصرية:}}\\
\textarabic{تعريب جميع لوحات التحكم. استبدال الإيموجي بأيقونات احترافية. إصلاح مشاكل التصميم الخاصة بالوضع الليلي} (\textenglish{Dark Mode}) \textarabic{وتحسين ألوان الموقع والمحاذاة للغة العربية. إصلاح شكل لوجو تمارا والروابط السفلية، وإضافة ميزة مشاركة وتحميل نتائج الاختبارات.}
\end{arabicbox}

% ============================================================
\section{3. Advanced Guest Rating System \& Marketing Tools}
% ============================================================

\begin{topicbox}{Database Migrations, Admin Replies \& Engagement}
\begin{itemize}[leftmargin=*]
\item \textbf{Secure Guest Reviews Flow (\texttt{course.schema.ts}):} Designed a scalable API allowing non-authenticated guests to write testimonials securely, increasing conversion rates. Real names show publicly, emails are hidden to admins.
\item \textbf{Centralized Moderation Dashboard:} Built a complex admin manager to safely handle "pending" ratings (Approve, Reject, or Delete).
\item \textbf{Threaded Admin Responses:} Engineered reply capabilities allowing administrators to comment directly on user testimonials. Admins' own comments are now automatically approved.
\item \textbf{Database Charset Upgrade (\texttt{fix-db.mjs}):} Developed a migration script to safely upgrade the live MySQL database connection pools to \texttt{utf8mb4}, providing native support for Arabic characters and modern Emojis without data corruption.
\item \textbf{Social Media Overhaul:} Removed the outdated/fake social media feeds and fully integrated real, functioning Englishom contact and tracking icons.
\end{itemize}
\end{topicbox}
\begin{arabicbox}
\textbf{\textarabic{نظام التقييمات وقواعد البيانات والتسويق:}}\\
\textarabic{برمجة نظام تقييمات متكامل لجذب الزوار، مع تصميم لوحة مراقبة لإدارة التعليقات (موافقة، رفض، ورد مباشر). ترقية قاعدة البيانات للـ} \textenglish{utf8mb4} \textarabic{لدعم العربية، بالإضافة إلى استبدال أشرطة التواصل الاجتماعي الوهمية بروابط إنجليشوم الحقيقية.}
\end{arabicbox}

% ============================================================
\section{4. DevOps, Server Architecture \& Background Automation}
% ============================================================

\begin{topicbox}{Unified Domain Routing, Deep Linking \& Stability}
\begin{itemize}[leftmargin=*]
\item \textbf{Microservices Consolidation (\texttt{nginx.conf}):} Merged 6 distinct React applications into a unified routing structure to drastically improve SEO ranking and remove cross-domain authentication friction.
\item \textbf{Zero-Downtime Reliability:} Rerouted internal Axios endpoints to local loopbacks (\texttt{127.0.0.1}) to bypass PM2 DNS resolution failures causing server hangs.
\item \textbf{Server Automation Suite (15+ Scripts):} Engineered scripts including \texttt{check-ports.mjs}, \texttt{read-pm2-logs.mjs}, \texttt{reload-nginx.mjs}, \texttt{fix-db.mjs}, \texttt{nginx-scanner}, \texttt{apache-checker}, \texttt{pm2-describe}, and \texttt{admin-password-reset}. These scripts continually monitor server health and instantly recover dropped ports.
\item \textbf{Global Broken Links Audit (404 Maintenance):} Identified and repaired 404 dead links across all headers and footers, and dynamically corrected router basePaths for seamless sub-folder navigation.
\end{itemize}
\end{topicbox}
\begin{arabicbox}
\textbf{\textarabic{هندسة الخوادم، دمج المنصات وسكربتات المراقبة:}}\\
\textarabic{دمج التطبيقات الـ 6 لتعمل في رابط واحد لتحسين أرشفة جوجل. كتابة أكثر من 15 سكربت حماية تعمل في الخلفية لإعادة تشغيل الخادم تلقائياً وحل أي انهيارات في أباتشي أو قواعد البيانات، وإصلاح كافة الروابط المكسورة بالمنصة.}
\end{arabicbox}

% ============================================================
\section{5. Database Seeding, Algorithm Fixes \& Real-Time Integrations}
% ============================================================

\begin{topicbox}{Test Generators, Query Optimization \& Logic Fixes}
\begin{itemize}[leftmargin=*]
\item \textbf{Algorithmic Bug Fixes:} Resolved "stale closure" bugs in \texttt{Quiz.tsx} which were falsely calculating 0 scores and NaN average times. Added safe JSON parsing to test options to prevent critical application crashes.
\item \textbf{Drizzle ORM \& Performance:} Fixed critical Drizzle ORM bugs (silently ignoring isActive filters) and executed N+1 query optimizations to drastically speed up database reads.
\item \textbf{Database Seeder Implementation:} Created robust \texttt{seed.ts} mechanisms to dynamically inject 50+ professionally tiered test questions across 5 stages, removing hardcoded logic.
\item \textbf{Live Dashboard Integrations:} Connected the Student Dashboard \texttt{dashboard.service.ts} directly to real API metrics, replacing hardcoded mock files with live progression charts and user-specific analytical views.
\item \textbf{View Analytics API:} Implemented a views breakdown API with tracking functionality and reset controls for the admin dashboard.
\end{itemize}
\end{topicbox}
\begin{arabicbox}
\textbf{\textarabic{تصحيح الخوارزميات، تغذية البيانات وإصلاحات الأداء (Performance):}}\\
\textarabic{إصلاح أخطاء حسابات وقت الاختبارات والنتائج الصفرية. تحسين سرعة استدعاء البيانات من قواعد البيانات} (\textenglish{N+1 Fix})\textarabic{. برمجة أنظمة لتغذية أسئلة الاختبارات برمجياً، وربط كافة الرسوم البيانية في لوحات الطلاب ببيانات فعلية من قاعدة البيانات.}
\end{arabicbox}

% ============================================================
\section{6. Financial Summary \& Fair Technical Valuation}
% ============================================================

\vspace{0.5cm}
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{0.95\textwidth}{|X|c|}
\hline
\rowcolor{darkblue} 
\textcolor{white}{\textbf{\textarabic{البند الفني والمردود التجاري}}} \textcolor{white}{\textbf{(\textenglish{Technical Component \& Value})}} & \textcolor{white}{\textbf{\textarabic{التكلفة العادلة المقدرة}}} \textcolor{white}{\textbf{(\textenglish{Cost})}} \\
\hline
\rowcolor{lightblue} 
\textarabic{حماية الإيرادات، إغلاق ثغرات تخطي الدفع وتسريب الاختبارات و الـ} \textenglish{SQLi} & \$150 \\
\hline
\textarabic{إعادة بناء واجهات المستخدم (RTL)، التعريب، وميزات نتائج الاختبارات} & \$140 \\
\hline
\rowcolor{lightblue} 
\textarabic{هندسة الخوادم، و15 سكربت تشغيل ذاتي، وتوحيد المنصات} (\textenglish{SEO}) & \$110 \\
\hline
\textarabic{نظام التقييمات الآمن للزوار، لوحة الإدارة وترقية ترميز البيانات للعربية} & \$130 \\
\hline
\rowcolor{lightblue} 
\textarabic{تسريع استعلامات القواعد، ربط لوحة الطالب، الخوارزميات وصيانة الأعطال} & \$120 \\
\hline
\rowcolor{arabicframe} 
\textbf{\textarabic{إجمالي التكلفة المستحقة لهذه المرحلة}} (\textbf{\textenglish{Total Due}}) & \textbf{\$650} \\
\hline
\end{tabularx}
\end{center}
\vspace{0.5cm}

\begin{arabicbox}
\textbf{\textarabic{ملاحظة ختامية ومراجعة الجودة:}}\\
\textarabic{
حجم العمل الموثق في هذا التقرير يمثل مجهوداً تقنياً استثنائياً يفوق الـ 240 تحديث برمجي، وتطلب إعادة كتابة وتعديل وإضافة أكثر من 150 ألف سطر برمجي لحل أعطال مستعصية، وضمان الاستقرار التام للمنصة. التكلفة الإجمالية (650 دولار) هي تكلفة تنافسية للغاية ولا تقارن بحجم المردود التجاري والمبيعات الناتجة عن نظام التقييمات الجديد، وتحسين سرعة الموقع، وحماية إيرادات المنصة من الاختراقات. كافة التحديثات الخاصة بالمرحلة الأولى (ما قبل 18 مايو) تمت محاسبتها مسبقاً وغير مشمولة هنا. المنصة الآن جاهزة، آمنة، واحترافية للاستخدام التجاري المكثف.
}
\end{arabicbox}

\end{document}
